1. Read the HTML content of the following URL with a variable called 
webpage: https://money.cnn.com/data/us_markets/ At this point, it will also be useful to open this web page in your browser.
```{r}
library(rvest)
webpage<-read_html(x = "https://money.cnn.com/data/us_markets/")
```
2. Get the session details (status, type, size) of the above mentioned URL.
```{r}

html_session("https://money.cnn.com/data/us_markets/")
```
3. Extract all of the sector names from the “Stock Sectors” table (bottom left of the web page.)
```{r}

html_text(html_nodes(webpage,"a[href*= sector]"))
```
4. Extract all of the “3 Month % Change” values from the “Stock Sectors” table.
```{r}

html_text(html_nodes(webpage, ".pctChange" ))
```
5. Extract the table “What’s Moving” (top middle of the web page) into a data-frame.
```{r}

html_table(html_nodes(webpage,"a[href* = div.wsod_fRight]" ))
```
6. Re-construct all of the links from the first column of the “What’s Moving” table.
```{r}
paste("https://money.cnn.com" ,html_attr(html_nodes(webpage,"td .wsod_symbol"),"href"))
```
Hint: the base URL is “https://money.cnn.com”
7. Extract the titles under the “Latest News” section (bottom middle of the web page.)
```{r}
html_text(html_nodes(webpage, "div.HeadlineList a"))
```
8. To understand the structure of the data in a web page, it is often useful to know what the underlying attributes are of the text you see.
```{r}
html_attrs(html_nodes(webpage,".wsod_StockTimestamp"))

```
Extract the attributes (and their values) of the HTML element that holds the timestamp underneath the “What’s Moving” table.
9. Extract the values of the blue percentage-bars from the “Trending Tickers” table (bottom right of the web page.)
```{r}
html_attr(html_nodes(webpage,".scale div"))
  
```
