# pre-class

### Question 1: Standardize Function

## A. Create a function called standardize.me() that takes a numeric vector as an argument, and returns the standardized version of the vector. 

```{r}
 standardize.me <- function(x) {
   
   output_x <- (x - mean(x)) / sd(x)
   
   return(output_x)
```
   
 }


## B. Assign all the numeric columns of the original WCGS dataset to a new dataset called WCGS.new.

```{r}
 WCGS.new <- wcgs%>%
  select(age,height,weight,sbp,dbp,chol,ncigs,bmi)
```

## C. Using a loop and your new function, standardize all the variables WCGS.new dataset.

``` {r}
for(j in 1:ncol(WCGS.new)) {
  
  WCGS.new[,j] <- standardize.me(WCGS.new)
  
  
}

```

D. What should the mean and standard deviation of all your new standardized variables be? Test your prediction by running a loop

```{r}
for(j in 1 :ncol(WCGS.me){
mean(WCGS.new[,j],
sd(WCGS.new[,j]
}
```




### Question 2: Looping to Calculate

A. Using a loop, calculate the mean weight of the subjects separated by the type of CHD they have.
B. Now do the same thing, but now don’t use a loop

